Spatiotemporal models of species biomass with time-varying DO

### 2019-09-11 analysis/VOCC/1-biomass-do-models-fixed-both.Rmd
log DO and filter DO outliers

Species
```{r}
species <- params$species

# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
 species <- "Quillback Rockfish"
# species <- "Pacific Ocean Perch"
# species <- "Yelloweye Rockfish"
```

@@

Choose model details
```{r}
# priors <- FALSE
 priors <- TRUE
# covariates <- "+muddy+any_rock"
 covariates <- ""
# covariates <- "+muddy+mixed+rocky"
# covariates <- "+mixed+rocky"
# covariates <- "+trawled+muddy+rocky+mixed"
# covariates <- "+trawled+mixed+rocky"
# covariates <- "+trawled+mixed"
covs <- gsub("\\+", "-", covariates)
covs <- "-both-tv-depth"
```

@@

  # scale predictors before filtering to ensure mean and SD are global
  data <- data %>% mutate(raw_depth = depth_bath, depth = log(raw_depth), temp = temperature_c) 
  do_data <- scale_predictors(data, predictors = c(quo(depth), quo(temp), quo(do_mlpl)))
       # c(quo(log_depth), quo(mixed), quo(muddy), quo(sandy), quo(rocky), quo(any_rock)))
  data <- do_data %>% mutate(depth = raw_depth) %>% #filter(year != 2016) %>%
    filter(ssid %in% model_ssid) %>% 
    filter(!is.na(do_mlpl)) %>% filter(!is.na(depth_scaled)) %>% filter(!is.na(temp))%>% 
    select(X, Y, X10, Y10, adult_density, imm_density, depth_scaled, depth_scaled2, depth_mean, depth_sd, do_mlpl_scaled, do_mlpl_scaled2,  do_mlpl_mean, do_mlpl_sd, temp_scaled, temp_scaled2, temp_mean, temp_sd, trawled, any_rock, muddy, sandy, year, ssid, fishing_event_id, depth, do_mlpl) %>% filter(!is.na(depth_scaled)) 
```

@@

    saveRDS(adult_biomass_d, 
      file = paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
        ))

@@

    saveRDS(imm_biomass_d, 
      file = paste0("data/", spp, 
        "/mod-imm-biomass-", spp,"-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
        ))

@@

    saveRDS(total_biomass_d, file = paste0("data/", spp, 
      "/model-total-biomass-", spp, "-fixed-do", covs, "-", ssid_string, "-prior-", priors, ".rds"
      ))
  }
```

>>>>

Species
```{r}
# species <- params$species

# # Species run so far...
# species <- "Arrowtooth Flounder"
# species <- "Petrale Sole"
# species <- "English Sole"
# species <- "Dover Sole" # maturity data error for WCHG
# species <- "Southern Rock Sole"
# species <- "Flathead Sole"

# species <- "Silvergray Rockfish"
# species <- "Quillback Rockfish" # summer-birthing
# species <- "Yelloweye Rockfish" # summer-birthing, overfished, 
# species <- "Bocaccio" # winter-birthing, overfished
# species <- "Sharpchin Rockfish"
# species <- "Splitnose Rockfish"

# species <- "Rougheye/Blackspotted Rockfish Complex"
# species <- "Redbanded Rockfish"
# species <- "Greenstriped Rockfish"
# # species <- "Copper Rockfish" # small sample
# species <- "Darkblotched Rockfish"
# # species <- "Shortbelly Rockfish" # small sample

# species <- "Pacific Ocean Perch" # schooling
# species <- "Widow Rockfish" # schooling
# species <- "Yellowtail Rockfish" # schooling
# species <- "Canary Rockfish" # schooling, winter-birthing

# species <- "Longspine Thornyhead"
# species <- "Shortspine Thornyhead"

# species <- "Walleye Pollock"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Lingcod"
# species <- "Pacific Hake"

# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Longnose Skate"
# species <- "Big Skate"
# species <- "Spotted Ratfish"
# species <- "Sandpaper Skate"
# species <- "Brown Cat Shark"
```

@@

Choose model details
```{r}
# priors <- FALSE
 priors <- TRUE
# covariates <- "+muddy+any_rock"
 covariates <- ""
# covariates <- "+trawled+as.factor(ssid)"
# covariates <- "+muddy+mixed+rocky"
# covariates <- "+mixed+rocky"
# covariates <- "+trawled+muddy+rocky+mixed"
# covariates <- "+trawled+mixed+rocky"
# covariates <- "+trawled+mixed"
# covs <- gsub("\\+", "-", covariates)
# covs <- "-both-tv-depth-ssid"
# covs <- "-both-tv-depth"
covs <- "-log-do"
```

@@

  # scale predictors before filtering to ensure mean and SD are global
  data <- data %>% mutate(raw_depth = depth_bath, depth = log(raw_depth), temp = temperature_c, raw_do = do_mlpl, do_mlpl = log(do_mlpl)) 
  do_data <- scale_predictors(data, predictors = c(quo(depth), quo(temp), quo(do_mlpl))) 
       # c(quo(log_depth), quo(mixed), quo(muddy), quo(sandy), quo(rocky), quo(any_rock)))
  data <- do_data %>% mutate(depth = raw_depth) %>% #filter(year != 2016) %>%
    filter(ssid %in% model_ssid) %>% 
    filter(!is.na(depth_scaled)) %>% filter(!is.na(do_mlpl)) %>% filter(!is.na(temp))

if (any(names(data) == "adult_density")) { 
  data <- data %>% select(X, Y, X10, Y10,
      adult_density, imm_density,
      depth_scaled, depth_scaled2, depth_mean, depth_sd, 
      do_mlpl_scaled, do_mlpl_scaled2,  do_mlpl_mean, do_mlpl_sd, 
      temp_scaled, temp_scaled2, temp_mean, temp_sd, 
      trawled, any_rock, muddy, sandy, year, ssid, fishing_event_id, 
      depth, do_mlpl, raw_do) 
 } else {
    data <- data %>% select(X, Y, X10, Y10,
      density,
      depth_scaled, depth_scaled2, depth_mean, depth_sd, 
      do_mlpl_scaled, do_mlpl_scaled2,  do_mlpl_mean, do_mlpl_sd, 
      temp_scaled, temp_scaled2, temp_mean, temp_sd, 
      trawled, any_rock, muddy, sandy, year, ssid, fishing_event_id, 
      depth, do_mlpl, raw_do) 
 }

 data <- filter(data, !(year == 2016 & ssid == 4) ) # 2016 do an outlier for survey 4
# unique(data$year)
# table(data$year,data$ssid)
```

@@

    saveRDS(adult_biomass_d, 
      file = paste0("data/", spp, 
        "/mod-mat-biomass-", spp,"-fixed", covs, "-", ssid_string, "-prior-", priors, ".rds"
        ))

@@

    saveRDS(imm_biomass_d, 
      file = paste0("data/", spp, 
        "/mod-imm-biomass-", spp,"-fixed", covs, "-", ssid_string, "-prior-", priors, ".rds"
        ))

@@

    saveRDS(total_biomass_d, file = paste0("data/", spp, 
      "/model-total-biomass-", spp, "-fixed", covs, "-", ssid_string, "-prior-", priors, ".rds"
      ))
  }
```
